Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-21 aa workingdraft/draft.tex
combining two param tables

\begin{table}[H]
\caption{Experimental and natural parameter ranges. Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity, bogen1992sedsize, wright2018hydrological}. Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
\centering
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Flow velocity (\SI{}{\centi\metre/\second})     
& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
Flow depth (\SI{}{\centi\metre})                
& 40          & 14--17      & 12           & 0--50     \\
\midrule
Collector diameter (\SI{}{\centi\metre})
& 0.318       & 0.3         & 0.63         & 0.1--1.2  \\
Collector Reynolds number                       
& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
Collector density ($\#/m^2$)
& 280--1450   & 2724--7209  & 1013--4053   & 10--2700  \\
Frontal area density, $a$ (\SI{}{\per\meter})
&             &             &              &           \\ 
Solid volume fraction, $\phi_c$ 
&             &             &              &           \\ 
\midrule
Specific gravity      
& 1.53        &2.27--2.61*  & 1.03         & 2.56--2.87\\
Particle diameter (\SI{}{\micro\metre})     
& 0.7--250    &1.25--250    & 212--250     & <2--250   \\
Suspended concentration (\SI{}{\micro\liter/\liter})      
&             &             &              &           \\
\midrule
Particle-collector diameter ratio, $R$      
&             &             &              &           \\
\bottomrule
\label{tbl:parameters}
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\caption{Experimental and natural parameter ranges. Natural values are approximations from other studies and literature reviews \cite{Nepf_2012,kadlec1990, czuba2015sedgravity, bogen1992sedsize, wright2018hydrological}. The asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
\centering
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Flow velocity (\SI{}{\centi\metre/\second})     
& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
Flow depth (\SI{}{\centi\metre})                
& 40          & 14--17      & 12           & 0--50     \\
\midrule
Collector shape
& Cylindrical & Artificial grass  & Cylindrical & -- \\ 
Collector diameter (\SI{}{\centi\metre})
& 0.318       & 0.3         & 0.6          & 0.1--1.2  \\
Collector Reynolds number                       
& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
Collector density ($\#/m^2$)
& 278--1450   & 2724--7209  & 1013--4053   & 10--2700  \\
Solid volume fraction, $\phi_c$ (\%)
& 0.22--1.17  & 0.82--2.16  & 2.86--11.5   & 0.1--45  \\ 
\midrule
Particle type
& Walnut shell flour  & Road dust  & Pliolite    & -- \\ 
Specific gravity      
& 1.53        &2.27--2.61*  & 1.03         & 2.56--2.87\\
Particle diameter (\SI{}{\micro\metre})     
& 0.7--250    &1.25--250    & 212--250     & <2--250   \\
Suspended concentration (\SI{}{\micro\liter/\liter})      
&             &             &              &           \\
\midrule
Particle-collector diameter ratio, $R$      
&             &             &              &           \\
\bottomrule
\label{tbl:parameters}
\end{tabular}
\end{table}
